---
title: "Children's satisfaction with education"
description: |
  Variable harmonization
# author:
#   - name: 
#     url: 
#     affiliation: 
#     affiliation_url:
# date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r initial, include=FALSE}
Sys.setlocale("LC_ALL", "English")
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```

# Set-up

The following packages are necessary for importing, managing, and harmonization of data:

````{r setup}
library(haven)  # Import foreign statistical formats
library(labelled)  # Functions to manipulate variable labels, value labels and missing values
library(tidyverse)  # Suite of packages for data management
library(questionr)  # Helps with frequency tables
library(writexl)  # Export to Excel
library(readxl)  # Importing from Excel
````


# Data import

The first task is to import the data. At this time, only the relevant variable is imported. Before being finalized, the technical (eg. weights, identifiers) and demographic variables must be added. Where possible, the SPSS file format is preferred, since it comes with variable and value labels that are easy to extract. 

````{r import}
basic_vars <- c("table_name")  # Other possibilities: "table_name", "Tcountry", "Sid", "Tid", "Tweight", "Tround", "Tyear"

# British Household Panel Study (BHPS)  
setwd("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/British Household Panel Study (BHPS)/SPSS BHPS Wave 1-18/UKDA-5151-spss/spss/spss19")
bhps_1994 <- read_sav("./bhps_w4/dyouth.sav", col_select="dyphsw", user_na=TRUE) %>%
  mutate(table_name = "BHPS_1994")
bhps_1995 <- read_sav("./bhps_w5/eyouth.sav", col_select="eyphsw", user_na=TRUE) %>%
  mutate(table_name = "BHPS_1995")
bhps_1996 <- read_sav("./bhps_w6/fyouth.sav", col_select="fyphsw", user_na=TRUE) %>%
  mutate(table_name = "BHPS_1996")
bhps_1997 <- read_sav("./bhps_w7/gyouth.sav", col_select="gyphsw", user_na=TRUE) %>%
  mutate(table_name = "BHPS_1997")

# More datasets 

````

# Prepare harmonization variables

The next stage is the preparation of the variables for harmonization. In this step, we create a codebook with a list of source variable names, value labels, any additional info (eg. categorical vs continuous coding), and the source data. We first need a function that will extract the information we need and then combine the information together into a list.


````{r harm_prep_fun}
create_codebook <- function(data) {
  var_labels <- data.frame(cbind(names(var_label(data)), do.call(rbind, var_label(data)))) %>%
    rename(varname = X1, varlabel = X2)
  freqs <- lapply(data, function(x) { return(questionr::freq(x)) }) %>%
    keep(function(x) nrow(x) < 1000) %>%
    do.call(rbind, .) %>% 
    tibble::rownames_to_column(var = "varname_value") %>%
    mutate(varname = gsub("(.+?)(\\..*)", "\\1", varname_value),
           value = gsub("^[^.]*.","",varname_value)) %>%
    group_by(varname) %>%
    mutate(npos = row_number(),
           value_n = paste(value, n, sep = ": ")) %>%
    select(varname, value_n, npos) %>%
    spread(npos, value_n) %>%
    mutate_at(vars(-varname), funs(ifelse(is.na(.), "", .))) %>%  # This line (funs()) needs to be updated
    unite("valfreqs", c(2:ncol(.)), sep = "\n") %>%
    mutate(valfreqs = sub("\\s+$", "", valfreqs))
  full_join(var_labels, freqs, by = "varname")
}
````

Then we extract the information from each of the datasets using our new function:


````{r harm_prep_comb}
codebook_bhps_1994 <- create_codebook(bhps_1994) %>%
    mutate(table_name = "BHPS_1994")
codebook_bhps_1995 <- create_codebook(bhps_1995) %>%
    mutate(table_name = "BHPS_1995")
codebook_bhps_1996 <- create_codebook(bhps_1996) %>%
    mutate(table_name = "BHPS_1996")
codebook_bhps_1997 <- create_codebook(bhps_1997) %>%
    mutate(table_name = "BHPS_1997")
# Continue with all datasets
````


The individual codebooks can then be combined together and exported to Excel.

````{r harm_prep_writecb}
codebook_all <- bind_rows(codebook_bhps_1994, codebook_bhps_1995, codebook_bhps_1996, codebook_bhps_1997) %>%
  mutate(target_var = NA)  # Continue with all datasets
write_xlsx(codebook_all, "ch_EDsati_1_codebook.xlsx")
````

The codebook can now be examined. Each row in the Excel file corresponds to one dataset. The following fields are displayed in the columns:  

* `varname` is the name of the variable in the original dataset
* `varlabel` is the label of the variable in the original dataset
* `valfreqs` is the frequency for each value in the original dataset
* `table_name` is the abbreviated name of of the original dataset
  
The table looks like this:

```{r, layout="l-body-outset"}
rmarkdown::paged_table(codebook_all)
```

  
# Create a crosswalk table

The next step is to map the input values to target values using a so-called crosswalk table. Start by importing the Excel table created in the previous step:

````{r harm_readcb}
setwd("I:/Team_IntUm/COORDINATE/D4.3-Harmonization/2_Education/ch_EDsati_1")
cb <- read_xlsx("ch_EDsati_1_codebook.xlsx")

create_cwt <- function(data) {
  var_labels <- data.frame(cbind(names(var_label(data)), do.call(rbind, var_label(data)))) %>%
    rename(varname = X1, varlabel = X2)
  freqs_cwt <- lapply(data, function(x) { return(questionr::freq(x)) }) %>%
    keep(function(x) nrow(x) < 1000) %>%
    do.call(rbind, .) %>% 
    tibble::rownames_to_column(var = "varname_value") %>%
    mutate(varname = gsub("(.+?)(\\..*)", "\\1", varname_value),
           value = gsub("^[^.]*.","",varname_value),
           value_code = sub(".*\\[(.+)\\].*", "\\1", varname_value, perl = TRUE),
           value_code = ifelse(str_sub(varname_value, -2, -1) == "NA", "NA", value_code), value_code = ifelse(gsub(" ", "", fixed = TRUE, varname_value) == varname_value, gsub("^[^.]*.","",varname_value), value_code)) %>%
    group_by(varname) %>%
    mutate(npos = row_number(),
           value_n = paste(value, n, sep = ": ")) %>%
    select(npos, varname, value_n, value, value_code)
  full_join(var_labels, freqs_cwt, by = "varname")
}

data_tables <- c("BHPS_1994", "BHPS_1995", "BHPS_1996", "BHPS_1997")
cwt_all <- list()
for (i in (1:length(data_tables))) {
  table_name_input <- data_tables[i]
  varnames <- cb$varname[cb$table_name == table_name_input]
  cwt_all[[i]] <- eval(parse(text = tolower(table_name_input))) %>%
    select(varnames) %>%
    create_cwt() %>%
    mutate(table_name = table_name_input)
}

cwt_all <- do.call(rbind, cwt_all) 

cwt_all %>%
  select(-varlabel) %>%
  left_join(cb, by = c("varname", "table_name")) %>%
  mutate(target_value = NA) %>%
  select(table_name, target_var,
         varname, varlabel, starts_with("c_"),
         value_n, value_code, target_value) %>%
  write_xlsx(., "cwt_all.xlsx")
````
  
We now have a new table that shows the values of the original variables as well as an empty column that can be used to map on the new variable values

```{r, layout="l-body-outset"}
rmarkdown::paged_table(cwt_all)
```

# Harmonization

Now we are ready to harmonize the concept of satisfaction with education. First we need a function to bring all the variables together:

````{r harm_fun}
setwd("I:/Team_IntUm/COORDINATE/D4.3-Harmonization/2_Education/ch_EDsati_1")
cwt_all1 <- readxl::read_xlsx("cwt_all.xlsx")
harmonize <- function(table_name_input, cwt_name_input) {
  target_vars <- unique(eval(parse(text = tolower(cwt_name_input)))$target_var[eval(parse(text = tolower(cwt_name_input)))$table_name == table_name_input])
  source_vars <- unique(eval(parse(text = tolower(cwt_name_input)))$varname[eval(parse(text = tolower(cwt_name_input)))$table_name == table_name_input])
  data_small <- eval(parse(text = tolower(table_name_input))) %>%
    select(basic_vars, source_vars) %>%
    zap_labels()
  harmonized_vars <- list()
  for (i in 1:length(target_vars)) {
    target_var_input = target_vars[i]
    source <- eval(parse(text = tolower(cwt_name_input))) %>% 
      filter(target_var == target_var_input, table_name == table_name_input) %>%
      pull(value_code)
    target <- eval(parse(text = tolower(cwt_name_input))) %>% 
      filter(target_var == target_var_input, table_name == table_name_input) %>%
      pull(target_value)
    source_varname <- eval(parse(text = tolower(cwt_name_input))) %>%
      filter(target_var == target_var_input, table_name == table_name_input) %>%
      pull(varname) %>% .[1]
    harmonized_vars[[i]] <- data_small %>%
      mutate(!!target_var_input := as.numeric(plyr::mapvalues(as.character(get(source_varname)), 
      source, target))) %>%
      select(basic_vars, target_var_input)
  }
  Reduce(merge, harmonized_vars)
}
````

And finally, the datasets can be harmonized together using the crosswalk table values indicated above.

````{r harm_, eval=FALSE}
bhps94_h <- harmonize("BHPS_1994", "cwt_all1")
````