---
title: "Variable harmonization"
description: |
  Children's subjective happiness
# author:
#   - name: 
#     url: 
#     affiliation: 
#     affiliation_url:
# date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r initial, include=FALSE}
Sys.setlocale("LC_ALL", "English")
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```

# Set-up

The following packages are necessary for importing, managing, and harmonization of data:

````{r setup}
library(haven)  # Import foreign statistical formats
library(labelled)  # Functions to manipulate variable labels, value labels and missing values
library(tidyverse)  # Suite of packages for data management
library(questionr)  # Helps with frequency tables
library(writexl)  # Export to Excel
library(readxl)  # Importing from Excel
````


# Data import

The first task is to import the data. At this time, only the relevant variable is imported. Before being finalized, the technical (eg. weights, identifiers) and demographic variables must be added. Where possible, the SPSS file format is preferred, since it comes with variable and value labels that are easy to extract. 


