---
title: "Material Wellbeing"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
library(readxl)
library(tidyverse)
library(knitr)
library(kableExtra)
```

Economic conditions play an important role in the well-being of Children. Evidence shows that children raised in economically disadvantaged families begin school behind peer and are negatively affected by this throughout their lives. Children’s material living standards are central to child wellbeing. For children, having access to basic material goods and activities is important in and of itself and is further related to other aspects of their lives. 

# Variables

## Household Income

Data from the International Survey of Children's Wellbeing show that over 20% of 8 year old children surveyed from across Europe are always worried about family finances.^[The data are drawn from the second wave of Children’s Worlds project (2016), an international survey of children’s lives and wellbeing. See https://isciweb.org/] Access to certain types of resources such as digital media and reading material are also central to children's development and conditional upon their family's material wellbeing.

```{r, fig.margin=TRUE, cache=TRUE}
ec <- haven::read_sav("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/Children's World (ISCWeB)/Data/Childrens worlds 2nd wave/ChildrensWorlds-Wave2-16Countries-8YO-060117.sav", col_select="FrequencyWorryFamilyMoney", user_na=FALSE)

df1 <- haven::as_factor(ec)

library(ggplot2)

p <- ggplot(na.omit(df1), aes(FrequencyWorryFamilyMoney))

p +
  geom_bar(aes(y = (..count..)/sum(..count..)), colour="red", fill="yellow") +
  scale_y_continuous(labels=scales::percent) +
  ylab("") +
  xlab("Proportion of 8 year olds who worry about money") +
  theme_classic()
```

## Household Characteristics

### Number of rooms in the household
**British Household Panel Study (BHPS)**
Link: to homepage

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!S7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Understanding Society (US)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AC7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Millenium Cohort Study (MCS)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AS9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AS7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Next Steps (LSYPE)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BA10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BA6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BA9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BA7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**British Cohort Survey 70 (BCS70)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BN9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BN7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Socio-Economic Panel Study Germany (SOEP)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CE10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CE6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CE9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CE7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DN7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Growing Up in Ireland (GUII) Infant Cohort**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DO10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DO6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DO9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DS9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DO7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DS7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Growing Up in Ireland (GUII) Child Cohort**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DT10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DT6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DT9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DT7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Growing Up in Scotland (GUIS) Birth Cohort 1**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DX10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DX6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DX9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EB9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DX7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EB7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Growing Up in Scotland (GUIS) Birth Cohort 2**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EG10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EG6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EG9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EI9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EG7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EI7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Etude Longitudinale Francaise depuis l'enfance (ELFE)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EK10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EK6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EK9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EM9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EK7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EM7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**National Child Development Study (NCDS)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EO10", col_names = FALSE)[[1]]`
Measurement           Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EO6", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EO9", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EQ9", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EO7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!EQ7", col_names = FALSE)[[1]]`
-------------------   ---------------------------

## Household electronic devices

**British Household Panel Study (BHPS)**
Link: to homepage

|               |                                    | 
|---------------|------------------------------------|      
| Question text | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B10", col_names = FALSE)[[1]]` |
| Measurement   | Ordinal                            |
| Perspective   | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B6", col_names = FALSE)[[1]]`|
| Age range     | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B9", col_names = FALSE)[[1]]`|
| Time span     | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!B7", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!S7", col_names = FALSE)[[1]]` |

**Understanding Society (US)**

|               |                                    | 
|---------------|------------------------------------|  
| Question text | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T22", col_names = FALSE)[[1]]` |
| Measurement   | Nominal                            |
| Perspective   | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T18", col_names = FALSE)[[1]]` |
| Age range     | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T21", col_names = FALSE)[[1]]` |
| Time span     | `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!T19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AC19", col_names = FALSE)[[1]]` |

**Children`s World (ISCWeB)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AD22", col_names = FALSE)[[1]]`
Measurement           Nominal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AD18", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AD21", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AL21", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AD19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AL19", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Millenium Cohort Study (MCS)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM22", col_names = FALSE)[[1]]`
Measurement           Nominal & Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM18", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM21", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AN21", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AM19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AN19", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Next Steps (LSYPE)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AT22", col_names = FALSE)[[1]]`
Measurement           Nominal & Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AV18", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AT21", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AW21", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AT19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!AW19", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**British Cohort Survey 70 (BCS70)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL22", col_names = FALSE)[[1]]`
Measurement           Nominal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL18", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL21", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BN21", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BL19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BN19", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Health Behaviour in School-Aged Children (HBSC)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BW22", col_names = FALSE)[[1]]`
Measurement           Nominal & Ordinal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BW18", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BW21", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BW19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!BZ19", col_names = FALSE)[[1]]`
-------------------   ---------------------------

**Socio-Economic Panel Study Germany (SOEP)**

-------------------   ---------------------------
Question text         `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CK22", col_names = FALSE)[[1]]`
Measurement           Nominal
Perspective           `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CK18", col_names = FALSE)[[1]]`
Age range             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CK21", col_names = FALSE)[[1]]`
Time span             `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!CK19", col_names = FALSE)[[1]]` -- `r read_excel("I:/Team_IntUm/COORDINATE/Harmonization Documentation/Harmonization-Documentation.xlsx", range="Material wellbeing!DH19", col_names = FALSE)[[1]]`
-------------------   ---------------------------



* Worries over family finances
* Access to reading material in the home



- Wave 1 (2011-2012) contains data from over 34000 children aged 8, 10, and 12 year old across 14 countries. [Wave 1 report](https://isciweb.org/the-data/wave-1-comparative-report/).
- Wave 2 (2013-2014) contains data from over 61000 children aged 8, 10, and 12 across 16 countries. [Wave 2 reports](https://isciweb.org/the-data/wave-2/).
- Wave 3 (2016-2019) contains data from over 128000 children aged 8, 10, & 12 across 35 countries. [Wave 3 reports](https://isciweb.org/the-data/wave-3/).

Data available here: https://isciweb.org/the-data/access-our-dataset/

[Alternative/addition: Link to an Excel file similar to what Laurenz is preparing that lists the measures from this variable]