---
title: "Variable harmonization"
description: |
  Children's satisfaction with education
# author:
#   - name: 
#     url: 
#     affiliation: 
#     affiliation_url:
# date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r initial, include=FALSE}
Sys.setlocale("LC_ALL", "English")
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 70)
)
```

# Set-up

The following packages are necessary for importing, managing, and harmonization of data:

````{r setup}
library(haven)  # Import foreign statistical formats
library(labelled)  # Functions to manipulate variable labels, value labels and missing values
library(tidyverse)  # Suite of packages for data management
library(questionr)  # Helps with frequency tables
library(writexl)  # Export to Excel
library(readxl)  # Importing from Excel
````

# Data import

The first task is to import the data. At this time, only the relevant variable is imported. Before being finalized, the technical (eg. weights, identifiers) and demographic variables must be added. Where possible, the SPSS file format is preferred, since it comes with variable and value labels that are easy to extract. 


````{r import}
# British Household Panel Study (BHPS)  
setwd("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/British Household Panel Study (BHPS)/SPSS BHPS Wave 1-18/UKDA-5151-spss/spss/spss19")
bhps_1994 <- read_sav("./bhps_w4/dhhresp.sav", col_select=c("dfihhyr", "dhid"), user_na=FALSE) %>%
  rename_with(.cols = dfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = dhid, ~"ID") %>%
  mutate(table_name = "bhps_1994")
bhps_1995 <- read_sav("./bhps_w5/ehhresp.sav", col_select=c("efihhyr", "ehid"), user_na=FALSE) %>%
  rename_with(.cols = efihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = ehid, ~"ID") %>%
  mutate(table_name = "bhps_1995")
bhps_1996 <- read_sav("./bhps_w6/fhhresp.sav", col_select=c("ffihhyr", "fhid"), user_na=FALSE)  %>%
  rename_with(.cols = ffihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = fhid, ~"ID") %>%
  mutate(table_name = "bhps_1996")
bhps_1997 <- read_sav("./bhps_w7/ghhresp.sav", col_select=c("gfihhyr", "ghid"), user_na=FALSE)  %>%
  rename_with(.cols = gfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = ghid, ~"ID") %>%
  mutate(table_name = "bhps_1997")
bhps_1998 <- read_sav("./bhps_w8/hhhresp.sav", col_select=c("hfihhyr", "hhid"), user_na=FALSE) %>%
  rename_with(.cols = hfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = hhid, ~"ID") %>%
  mutate(table_name = "bhps_1998")
bhps_1999 <- read_sav("./bhps_w9/ihhresp.sav", col_select=c("ifihhyr", "ihid"), user_na=FALSE) %>%
  rename_with(.cols = ifihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = ihid, ~"ID") %>%
  mutate(table_name = "bhps_1999")
bhps_2000 <- read_sav("./bhps_w10/jhhresp.sav", col_select=c("jfihhyr", "jhid"), user_na=FALSE) %>%
  rename_with(.cols = jfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = jhid, ~"ID") %>%
  mutate(table_name = "bhps_2000")
bhps_2001 <- read_sav("./bhps_w11/khhresp.sav", col_select=c("kfihhyr", "khid"), user_na=FALSE) %>%
  rename_with(.cols = kfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = khid, ~"ID") %>%
  mutate(table_name = "bhps_2001")
bhps_2002 <- read_sav("./bhps_w12/lhhresp.sav", col_select=c("lfihhyr", "lhid"), user_na=FALSE) %>%
  rename_with(.cols = lfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = lhid, ~"ID") %>%
  mutate(table_name = "bhps_2002")
bhps_2003 <- read_sav("./bhps_w13/mhhresp.sav", col_select=c("mfihhyr", "mhid"), user_na=FALSE) %>%
  rename_with(.cols = mfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = mhid, ~"ID") %>%
  mutate(table_name = "bhps_2003")
bhps_2004 <- read_sav("./bhps_w14/nhhresp.sav", col_select=c("nfihhyr", "nhid"), user_na=FALSE) %>%
  rename_with(.cols = nfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = nhid, ~"ID") %>%
  mutate(table_name = "bhps_2004")
bhps_2005 <- read_sav("./bhps_w15/ohhresp.sav", col_select=c("ofihhyr", "ohid"), user_na=FALSE) %>%
  rename_with(.cols = ofihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = ohid, ~"ID") %>%
  mutate(table_name = "bhps_2005")
bhps_2006 <- read_sav("./bhps_w16/phhresp.sav", col_select=c("pfihhyr", "phid"), user_na=FALSE) %>%
  rename_with(.cols = pfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = phid, ~"ID") %>%
  mutate(table_name = "bhps_2006")
bhps_2007 <- read_sav("./bhps_w17/qhhresp.sav", col_select=c("qfihhyr", "qhid"), user_na=FALSE) %>%
  rename_with(.cols = qfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = qhid, ~"ID") %>%
  mutate(table_name = "bhps_2007")
bhps_2008 <- read_sav("./bhps_w18/rhhresp.sav", col_select=c("rfihhyr", "rhid"), user_na=FALSE) %>%
  rename_with(.cols = rfihhyr, ~"pa_MWinco_1") %>%
  rename_with(.cols = rhid, ~"ID") %>%
  mutate(table_name = "bhps_2008")


# Understanding Society (US)
setwd("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/Understanding Society (US)/spss/UKDA-6614-spss/spss/spss25")
us_2009 <- read_sav("./ukhls_w1/a_hhresp.sav", col_select=c("a_fihhmngrs_dv", "a_hidp"), user_na=FALSE) %>%
  rename_with(.cols = a_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = a_hidp, ~"ID") %>%
  mutate(table_name = "us_2009")
us_2010 <- read_sav("./ukhls_w2/b_hhresp.sav", col_select=c("b_fihhmngrs_dv", "b_hidp"), user_na=FALSE) %>%
  rename_with(.cols = b_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = b_hidp, ~"ID") %>%
  mutate(table_name = "us_2010")
us_2011 <- read_sav("./ukhls_w3/c_hhresp.sav", col_select=c("c_fihhmngrs_dv", "c_hidp"), user_na=FALSE) %>%
  rename_with(.cols = c_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = c_hidp, ~"ID") %>%
  mutate(table_name = "us_2011")
us_2012 <- read_sav("./ukhls_w4/d_hhresp.sav", col_select=c("d_fihhmngrs_dv", "d_hidp"), user_na=FALSE) %>%
  rename_with(.cols = d_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = d_hidp, ~"ID") %>%
  mutate(table_name = "us_2012")
us_2013 <- read_sav("./ukhls_w5/e_hhresp.sav", col_select=c("e_fihhmngrs_dv", "e_hidp"), user_na=FALSE) %>%
  rename_with(.cols = e_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = e_hidp, ~"ID") %>%
  mutate(table_name = "us_2013")
us_2014 <- read_sav("./ukhls_w6/f_hhresp.sav", col_select=c("f_fihhmngrs_dv", "f_hidp"), user_na=FALSE) %>%
  rename_with(.cols = f_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = f_hidp, ~"ID") %>%
  mutate(table_name = "us_2014")
us_2015 <- read_sav("./ukhls_w7/g_hhresp.sav", col_select=c("g_fihhmngrs_dv", "g_hidp"), user_na=FALSE) %>%
  rename_with(.cols = g_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = g_hidp, ~"ID") %>%
  mutate(table_name = "us_2015")
us_2016 <- read_sav("./ukhls_w8/h_hhresp.sav", col_select=c("h_fihhmngrs_dv", "h_hidp"), user_na=FALSE) %>%
  rename_with(.cols = h_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = h_hidp, ~"ID") %>%
  mutate(table_name = "us_2016")
us_2017 <- read_sav("./ukhls_w9/i_hhresp.sav", col_select=c("i_fihhmngrs_dv", "i_hidp"), user_na=FALSE) %>%
  rename_with(.cols = i_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = i_hidp, ~"ID") %>%
  mutate(table_name = "us_2017")
us_2018 <- read_sav("./ukhls_w10/j_hhresp.sav", col_select=c("j_fihhmngrs_dv", "j_hidp"), user_na=FALSE) %>%
  rename_with(.cols = j_fihhmngrs_dv, ~"pa_MWinco_1") %>%
  rename_with(.cols = j_hidp, ~"ID") %>%
  mutate(table_name = "us_2018")



# Millenium Cohort Survey
setwd("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/Millenium Cohort Study (MCS)")
# Household and person identifier (no unique identifier in original data)
mcs_2004 <- read_stata("./Data & Documentation (Wave 2 - 2004 - 3 Years Old)/stata/stata13/mcs2_parent_interview.dta", col_select=c("BPGROA00", "MCSID", "BPNUM00")) %>%
  rename_with(.cols = BPGROA00, ~"pa_MWinco_1") %>%
  mutate(ID=paste0(MCSID, BPNUM00)) %>%
  mutate(table_name = "mcs_2004") %>%
  select(-c(MCSID, BPNUM00))
# Missing income info in this wave
# mcs_2006 <- read_stata("./Data & Documentation (Wave 3 - 2006 - 5 Years Old)/stata/stata13/mcs3_parent_interview.dta", col_select=c("CPGROA00", "MCSID", "CPNUM00")) %>%
#   rename_with(.cols = CPGROA00, ~"pa_MWinco_1") %>%
#   mutate(ID=paste0(MCSID, CPNUM00)) %>%
#   mutate(table_name = "mcs_2006") %>%
#   select(-c(MCSID, CPNUM00))
mcs_2008 <- read_dta("./Data & Documentation (Wave 4 - 2008 - 7 Years Old)/stata/stata13/mcs4_parent_interview.dta", col_select=c("DPGROA00", "MCSID", "DPNUM00")) %>%
  rename_with(.cols = DPGROA00, ~"pa_MWinco_1") %>%
  mutate(ID=paste0(MCSID, DPNUM00)) %>%
  mutate(table_name = "mcs_2008p") %>%
  select(-c(MCSID, DPNUM00))
mcs_2012 <- read_dta("./Data & Documentation (Wave 5 - 2012 - 11 Years Old)/stata/stata13/mcs5_parent_interview.dta", col_select=c("EPGROA00", "MCSID", "EPNUM00")) %>%
  rename_with(.cols = EPGROA00, ~"pa_MWinco_1") %>%
  mutate(ID=paste0("MCSID", "EPNUM00")) %>%
  mutate(table_name = "mcs_2012") %>%
  select(-c(MCSID, EPNUM00))
mcs_2015 <- read_dta("./Data & Documentation (Wave 6 - 2015 - 14 Years Old)/stata/stata13/mcs6_parent_interview.dta", col_select=c("FPGROA00", "MCSID", "FPNUM00")) %>%
  rename_with(.cols = FPGROA00, ~"pa_MWinco_1") %>%
  mutate(ID=paste0("MCSID", "FPNUM00")) %>%
  mutate(table_name = "mcs_2015") %>%
  select(-c(MCSID, FPNUM00))

# Next Steps (LYPSE)
setwd("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/Next Steps (LYPSE)/Data & Documentation Next Steps (LYPSE (Wave 1-8) (SPSS))/UKDA-5545-spss/spss/spss25/eul")
ns_2004 <- read_sav("./wave_one_lsype_family_background_2020.sav", col_select = c("W1inc2estMP", "NSID")) %>%
  rename_with(.cols = W1inc2estMP, ~"pa_MWinco_1") %>%  
  rename_with(.cols = NSID, ~"ID") %>%
  mutate(table_name = "ns_2004")
ns_2005 <- read_sav("./wave_two_lsype_family_background_2020.sav", col_select = c("W2Inc2estMP", "NSID")) %>%
  rename_with(.cols = W2Inc2estMP, ~"pa_MWinco_1") %>%
  rename_with(.cols = NSID, ~"ID") %>%
  mutate(table_name = "ns_2005")
#ns_2006 <- read_sav("./wave_three_lsype_family_background_2020.sav", col_select = c("W3incestMP", "NSID")) %>%
#  rename_with(.cols = W3incestMP, ~"pa_MWinco_1") %>%
#  rename_with(.cols = NSID, ~"ID") %>%
#  mutate(table_name = "ns_2006")
#ns_2007 <- read_sav("./wave_four_lsype_family_background_2020.sav", col_select = c("W4Inc1EstMP", "NSID")) %>%
#  rename_with(.cols = W4Inc1EstMP, ~"pa_MWinco_1") %>%
#  rename_with(.cols = NSID, ~"ID") %>%
#  mutate(table_name = "ns_2007")

# DJI
setwd("I:/Team_IntUm/COORDINATE/Source Surveys Data & Documentation/Deutsches Jugendinstitut Jugendsurvey (DJI)/Data")
dji_1997 <- read_dta("ZA3298.dta", col_select=c("JS53", "JF00_1")) %>%
  mutate(JS53 = replace(JS53, which(JS53>94L), NA)) %>%
  rename_with(.cols = JS53, ~"pa_MWinco_1") %>%
  rename_with(.cols = JF00_1, ~"ID") %>%
  mutate(table_name = "dji_1997")
## Potentially return to this. The response cats are in letters...?
# dji_2003 <- read_dta("ZA5187.dta", col_select=c("J505T", "lfd")) %>%
#   mutate(JS53 = replace(JS53, which(JS53>94L), NA)) %>%
#   rename_with(.cols = J505T, ~"pa_MWinco_1") %>%
#   rename_with(.cols = lfd, ~"ID") %>%
#   mutate(table_name = "dji_2003")
````

# Harmonization

First we bring the files together

````{r, harm1}
survey_files <- plyr::rbind.fill(bhps_1994, bhps_1995, bhps_1996, bhps_1997, bhps_1998, 
                                 bhps_1999, bhps_2000, bhps_2001, bhps_2002, bhps_2003, 
                                 bhps_2004, bhps_2005,  bhps_2006, bhps_2007, bhps_2008, 
                                 us_2009, us_2010, us_2011, us_2012, us_2013, us_2014, us_2015, 
                                 us_2016, us_2017, mcs_2008, mcs_2012, mcs_2015, 
                                 ns_2004, dji_1997)
````

Because household income is a quantitative variable, we will divide the incomes into country-specific deciles.

````{r, harm2}
# Scale to deciles
survey_files <- survey_files %>%
  mutate(pa_MWinco_1=replace(pa_MWinco_1, which(pa_MWinco_1<0L), NA)) %>%
  group_by(table_name) %>%
  mutate(pa_MWinco_1_harm = gtools::quantcut(pa_MWinco_1, q=10, na.rm=TRUE, labels=FALSE))


setwd("I:/Team_IntUm/COORDINATE/D4.3-Harmonization/1_Material/pa_MWinco_1")
saveRDS(survey_files, file="pa_MWinco_1_harm.Rds")

df <- readRDS("pa_MWinco_1_harm.Rds")
````
